The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-02-15 analysis/paper/paper.qmd
Update top n per corpus code chunk
Update top words code chunks

Counting frequencies of words per document
```{r}
# Which are the top n most frequently used words in each thesis?
top_n_word_count_per_document(data = emu_theses_words, 
                              top_n = 3, 
                              title_col = 'title', 
                              word_col = 'word')
```

```{r}
# Which are the top n most frequently used words in all theses`?
top_n_word_count_per_corpus(emu_theses_words, 5, "word")
```

```{r}
# Which are first 5 most frequently used words in each thesis?
emu_theses_first_5 <- emu_theses_words %>%
  count(title, word) %>% 
  group_by(title) %>% 
  arrange(desc(n)) %>% 
  slice(1:5)
```

>>>>

```{r}
# Which are the top n most frequently used words in each thesis?
top_n_word_count_per_document(data = emu_theses_words, 
                              top_n = 3, 
                              title_col = "title", 
                              word_col = "word")
```

```{r}
# Which are the top n most frequently used words in all theses`?
top_n_word_count_per_corpus(data = emu_theses_words, 
                            top_n = 5, 
                            word_col = "word")
```
